My title

### 2024-03-20 paper/paper.qmd
Citations page works now

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
execute:
  echo: FALSE 
---

@@

```{r}
##chooseCRANmirror(graphics = FALSE)  # Select a CRAN mirror
##install.packages("devtools")        # Install the devtools package
```

```{r}
##install.packages("devtools")
##install.packages("kableExtra")
##devtools::install_github("haozhu233/kableExtra")
```

@@

@@

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Michael Shmelev
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
bibliography: cite3.bib
format: pdf
number-sections: true
execute:
  echo: FALSE 
---

@@

@@

https://docs.google.com/forms/d/e/1FAIpQLSewSdOqUt17prCm287W3FgkCC8GdMWMrgYlAw6CTWbCxOa06g/viewform?usp=sf_link

@@

[@citeR]

[@tellingstories]
